THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-04-15 DishReflectometry/Paper1_v1.tex
Paper updated up to section 5

\section{Introduction}

@@

\section{Visibility measurements by a two element interferometer and the delay spectrum}
Consider a two element interferometer with a baseline $\vec b$. If we denote the electric field sky signal in direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$  then the voltage output of each antenna may be written as,  
\begin{equation}
\volt_{1}(\thhat, \nu) = \bmvolt_{1}(\thhat,\nu)\volt_\sky(\thhat,\nu)\nonumber\\
\end{equation}
\begin{equation}
\volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)\volt_\sky(\thhat,\nu)\fngexp\nonumber\\
\end{equation}
Hence, the time averaged visibility measured by the interferometer may be written as, 
\begin{equation}
\vis(\vec b, \nu) =  \int  \volt_{1}(\thhat,\nu)  \volt_{2}^{*} (\thhat, \nu) \ifngexp d\Omega 
\label{eq1}
\end{equation}

@@

\section{Effects of multiple reflections on visibility and delay spectrum}
The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER. Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. 
The reflected signal illuminates the dish and most of it is reflected back into the space.
However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (dashed blue arrows in Figure \ref{fig:cartoon}).
Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.  Identical spurious visibilities could be resulted due to reflections internal to the system causing delay space distortion. Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum. 
In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum, using the multiple reflection formulation of Sec. \ref{sec:multiple}. In this section, the effect of reflections on the visibility data and corresponding effect on the delay spectrum is discussed in detail. We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$. 
 \subsection{Antenna Reception With Multiple Reflections}
\label{sec:multiple}
To examine the performance of an antenna and feed in the presence of multiple reflections, think of the system as a screen at a distance $F$ from a feed (see Fig. \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.  The screen reflects voltage as $\Gamma_d$ and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed. 
Additionally however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
$n^{th}$ reflection may be written as:
\begin{eqnarray}
\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
\end{eqnarray}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{plots/microsys.pdf}
\caption{System}
\label{fig:sys}
\end{figure}

@@

% Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected. \\
In a related series of papers, (Thyagarajan et al 2016) has shown the detailed sensitivity calculations of HERA is using a comprehensive foreground as well as model for EoR power spectrum for various simulated antenna element response (\ref{fig:sim_limit_delay}) From this simulations, the figure \ref{fig:sim_limit_delay} (Thyagarajan et al) shows the level of attenuation required for the multiple reflected sky signal in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements. Ewall-Wice et al 2016 has simulated the time domain response of the HERA element considering multiple reflections between the feed and the dish.  Figure \ref{fig:sim_limit_delay} shows the simulated cross-power response of a pair of HERA antenna as a function of time(Ewall-wice et al). These simulations set up the performance criterion for the HERA antenna element.
 \begin{figure*}[ht]
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/sim_limit.jpg}
\end{minipage}
\hspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/sim_delay.jpg}
\end{minipage}
\caption{Left: Signal attenuation required for the reflected sky power arriving at the feed at higher delay as estimated from the simulated antenna beam and froeground models (Thyagarajan et al). The three different contour shows three different system performance requirements set based on the simulated response of HERA element for a measurement frequency of 150MHz corresponding to the redshift of $z=8.47$ and a 14.5m baseline. The instrumental requirements become extremely stringent for the detection of the smaller $k_\parallel$ values corresponding to very large spatial scales. Right: The simulated cross power response kernel for HERA. The simulation assumes and achromatic beam with the chromaticity attributed entirely by the multiple reflections between the dish and the feed. This shows the levels to which the multiple reflections at the higher delays is expected to be reduced following the dish and the feed design.}
\label{fig:sim_limit_delay}       
\end{figure*}

%signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
%at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
%signal at the feed ~\citep{parsons_deboer_memo}. This specification was
%approximated based on the power level of the cosmological signal in relation to
%foreground signals, which is estimated to be six orders of magnitude fainter
%~\citep{santos_et_al2005,  ali_et_al2008,deoliveira2008, jelic_et_al2008, bernardi_et_al2009,bernardi_et_al2010, ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
%Additionally, the $14m$ HERA baselines set a foreground containing
%horizon-limit (the wedge) that, with some buffer, sets a delay specification of
%$60ns$
%~\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}. Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements. 
%++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Reflectometry measurements}
\begin{figure*}
\centering
\includegraphics[trim={2cm 10cm 20cm 5cm},clip, totalheight=0.3\textheight]{plots/herafeed.jpg}
\vspace{1.0 em}
\caption{HERA feed consists of a pair of crossed dipole ove xxx mt diameter backplane made of wire mesh. The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the cross dipole in a cylindrical cage.}
\label{fig:herafeed}
\end{figure*}
Reflectometry measurements are carried out at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance.  HERA element consists off a $14\,m$ diameter
parabolic reflector and a crossed-dipole pair as a feed. The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles. HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter. Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage. The feed is raised and
lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  The detail geometry and electromagnetic design of of the feed is presented in deBoer et al 2016 (in prep). \\
A vector network analyser is connected via a 50feet long cable at the feed output of the HERA element and the return loss $(s_{11})$ of the HERA element is measured as a function of frequencies while the feed is suspended at the focal plane of the dish. This measurement is 
Section 3 laid the mathematical framework of how the delay spectrum is estimated from the return loss measurement. 
%, if the incident power from the sky signal is $I_{sky}$, the feed
%reflection coefficient is $\Gamma_{f}$, and the dish reflection
%coefficient is $\Gamma_{d}$, then the net power entering a feed after
%$n^{th}$ reflection off the feed and the dish is:

@@

Return loss measurements are similar to auto correlation measurement from a single HERA element. Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$. 
\section{Results}
\begin{figure*}[ht]
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/RL_mag.png}
\end{minipage}
\hspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/RL_phse.png}
\end{minipage}
\caption{Left: Magnitude of the return loss of power measured in between 100 to 200 MHz using vector network analyser. Right panel shows the corresponding phase. Return loss of the feed alone is shown in green while the same for the feed+dish assembly is shown in blue. Finally, the quantity of interest ${I_{rec}\over I_{sky}}$ is shown in red. In ideal condition 100\% of the sky power is to be received and ${I_{rec}\over I_{sky}} = 1$ or 0dB. Finite return loss at the antenna input deviate this quantity from its ideal value and ${I_{rec}\over I_{sky}} < 1$. Also, frequency dependence of the feed and the dish as well as the multiple reflections introduces the small scale fluctuations as shown in the red curve. }
% HERA feed design is derived from modified PAPER antenna and therefore the return loss closely relates to the PAPER antenna response with slight frequency shift. The return loss measured when the HERA feed is suspended over the dish is, however, show deviation from the feed performance. }
\label{fig:freq}       
\end{figure*}

Figure \ref{fig:freq} shows the return loss measured between $100$ to
$200MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex. This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}. Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution. A number of systematic effects as well as mathematical artefacts that are critical to this measurements and corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.

\subsection{Feed effect:zero delay correction}
%At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.

While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}. This essentially represents a mismatch in between the feed and the 50 Ohm transmission line. In delay domain, this appears at the zero delay bin. The zero delay response is identical whether or not the feed is suspended on the dish and  Therefore, we measure this response by measuring the feed return loss alone while the feed is kept on the ground facing the sky. This results in feed return loss alone including the surrounding cage structure but excluding the dish response. While $\Gamma_{f}$ fraction of power is reflected off the feed, $1+\Gamma_{f}$ fraction of the power gets transmitted. In receiving mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected back in to the space while $1+\Gamma_{f}$ voltage enters the feed. In receiving mode, in delay domain, this appears at the zero delay bin.
The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} for the zero delay component and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_BH.png}
\caption{Delay spectrum of the HERA element, the PAPER element and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output. HERA feed design is driven by the PAPER element with improved response at all delays. The feed, when suspended on the dish results in a more complex return loss and corresponding delay response is shown in the figure.}
\label{fig:delay_spectrum}
\end{figure}

\subsubsection{Effect of antenna beam pattern and feed return loss on delay spectrum estimation}
The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna. Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$. Since reflected signal results in system response in higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.  The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line. The complex feed antenna impedance is shown in the figure \ref{fig:feed_impedance}.
\begin{figure}
\centering
\includegraphics[width=\linewidth]{plots/Feed_impedance.png}
\caption{Complex antenna impedance of the HERA feed element.}
\label{fig:feed_impedance}
\end{figure} 
While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum. However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant. Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{fig:freq}. This provides the maximum impedance matching. \\
\subsubsection{Effect of frequency bandwidth on delay spectrum estimation}
Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the frequency bandwidth of operation. Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function. In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays. Therefore, appropriate windowing of the data is  necessary prior to taking the Fourier transform of the measured data. Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window. Windowing the data prior to Fourier transform significantly reduces the system response higher delays.  
\begin{figure}
\centering
\includegraphics[width=\linewidth]{plots/window.png}
\caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz. Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window. The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
\label{fig:window}
\end{figure} 
\subsubsection{Effect of dish and the feed on delay spectrum estimation}
Measurement equations shows the effects of multiple reflections of the sky signal between the feed and the dish. Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays. The estimated delay spectrum of the instrument is collectively contributed by all the reflections. We measure the return loss of the feed alone keeping it on the ground facing the sky shown in the Figure \ref{fig:freq}. Delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish. 
 Any additional reflections also contributes to the measured return loss and thus contributed to the delay spectrum at various delays. Figure \ref{fig:delay_spectrum} shows the delay spectrum of the feed while it is kept upside down on the ground in green, as well as that of a HERA antenna with the feed suspended at the focal plane in blue. Red line shows shows the delay spectrum of the PAPER antenna in comparison with the HERA element.
%\subsubsection{Effect of feed height on delay spectrum estimation}
\subsubsection{Comparison of performance of HERA with PAPER}
While PAPER has established the till date the most stringent upper limit on the 21cm power spectrum measurement, the need to increase the measurement sensitivity called for increased collecting area per PAPER antenna. This has driven to the parabolic reflector antenna based design of the PAPER successor HERA where essentially the PAPER antenna with minor modification of the ground plane-side plane assembly works as the feed and thus having larger collecting area per element. Figure \ref{fig:freq} shows the return loss measurement of power of the PAPER antenna and figure \ref{fig:delay_spectrum} shows (red line) the corresponding delay spectrum. The feed element shows improved delay response compared to the PAPER element across all delays $>50~ns$ with marginal improvement at delays $<50~ns$. The delay response of the HERA element degrades marginally as the feed is suspended over the dish due to multiple reflections between the feed and the dish.  It is evident that majority of the response at lower delays are contributed due to the feed and its supporting structure at lower delays which is somewhat common to all three measurements. At the lower delays, the structures in the delay response remains unaltered even with the variation of the feed height relative to the dish vertex. It is essentially these structures set lower limits on the $k_{||}$ that could be probed and any redshift $z$ above the instrument footprint.

\subsubsection{Comparison with simulations}
\section{Effect of instrument delay spectrum on 21cm power spectrum measurements }

The delay response of the instrument is dependent on the band chosen for the Fourier transform.
The measurement bandwidth effects the amplitude and phase of the delay spectrum. Fourier transforms taken over wider bandwidth
become dominated by the feed sidelobes outside the operating band, making the resultant delay profiles less relevant
for the power spectrum performance of the HERA instrument.  Conversely, when performing Fourier transforms over much 
narrow bands (the windowed $20MHz$ bands typical of PAPER analysis), the width of the resulting delay profile
becomes dominated by sidelobes of low delay emission interacting with the narrow bandwidth kernel.  
Although this may appear to be a relevant performance metric for PAPER power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid sidelobes from low-delay emission.  Hence, the most relevant delay-spectrum performance profile is that taken using the $100-200MHz$ band. \textbf{In the $100-200MHz$ delay profile, we see a delay response of $-25dB$ at $60ns$, which slopes down to $-60dB$ at $\sim120ns$.  WRITE AGAIN}

>>>>

\section{\textbf{Introduction}}

@@

\section{\textbf{Visibility measurements by a two element interferometer and the delay spectrum}}
Consider a two element interferometer with a baseline $\vec b$. If we denote the electric field sky signal in direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$  then the voltage output of each antenna may be written as,  
\begin{equation}
\volt_{1}(\thhat, \nu) = \bmvolt_{1}(\thhat,\nu)\volt_\sky(\thhat,\nu)\nonumber\\
\end{equation}
\begin{equation}
\volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)\volt_\sky(\thhat,\nu)\fngexp\nonumber\\
\end{equation}
Hence, the time averaged visibility measured by the interferometer may be written as, 
\begin{equation}
\vis(\vec b, \nu) =  \int  \volt_{1}(\thhat,\nu)  \volt_{2}^{*} (\thhat, \nu) \ifngexp d\Omega 
\label{eq1}
\end{equation}

@@

\section{\textbf{Effects of multiple reflections on visibility and delay spectrum}}
The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER. Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. 
The reflected signal illuminates the dish and most of it is reflected back into the space.
However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (dashed blue arrows in Figure \ref{fig:cartoon}).
Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.  Identical spurious visibilities could be resulted due to reflections internal to the system causing delay space distortion. Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum. 
In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum, using the multiple reflection formulation of Sec. \ref{sec:multiple}. In this section, the effect of reflections on the visibility data and corresponding effect on the delay spectrum is discussed in detail. We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$. 
 \subsection{\textbf{Antenna Reception With Multiple Reflections}}
\label{sec:multiple}
To examine the performance of an antenna and feed in the presence of multiple reflections, think of the system as a screen at a distance $F$ from a feed (see Fig. \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.  The screen reflects voltage as $\Gamma_d$ and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed. 
Additionally however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
$n^{th}$ reflection may be written as:
\begin{eqnarray}
\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
\end{eqnarray}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{plots/microsys.pdf}
\caption{System}
\label{fig:sys}
\end{figure}

@@

% Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected. \\

%signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
%at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
%signal at the feed ~\citep{parsons_deboer_memo}. This specification was
%approximated based on the power level of the cosmological signal in relation to
%foreground signals, which is estimated to be six orders of magnitude fainter
%~\citep{santos_et_al2005,  ali_et_al2008,deoliveira2008, jelic_et_al2008, bernardi_et_al2009,bernardi_et_al2010, ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
%Additionally, the $14m$ HERA baselines set a foreground containing
%horizon-limit (the wedge) that, with some buffer, sets a delay specification of
%$60ns$
%~\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}. Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements. 
%++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{\textbf{Reflectometry measurements}}
\begin{figure*}
\centering
\includegraphics[trim={2cm 10cm 20cm 5cm},clip, totalheight=0.3\textheight]{plots/herafeed.jpg}
\vspace{1.0 em}
\caption{HERA feed consists of a pair of crossed dipole ove xxx mt diameter backplane made of wire mesh. The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the cross dipole in a cylindrical cage.}
\label{fig:herafeed}
\end{figure*}
Reflectometry measurements are carried out at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance.  HERA element consists off a $14\,m$ diameter
parabolic reflector and a crossed-dipole pair as a feed. The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles. HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter. Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage. The feed is raised and
lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  The detail geometry and electromagnetic design of of the feed is presented in deBoer et al 2016 (in prep). \\
A vector network analyser is connected via a 50feet long cable at the feed output of the HERA element and the return loss $(s_{11})$ of the HERA element is measured as a function of frequencies while the feed is suspended at the focal plane of the dish. This measurement is 
Section 3 laid the mathematical framework of how the delay spectrum is estimated from the return loss measurement. The return loss of the feed while  facing up the sky as well as while suspended on the dish and ${I_{rec}\over I_{sky}}$  is shown in figure \ref{fig:all_RL}.
%, if the incident power from the sky signal is $I_{sky}$, the feed
%reflection coefficient is $\Gamma_{f}$, and the dish reflection
%coefficient is $\Gamma_{d}$, then the net power entering a feed after
%$n^{th}$ reflection off the feed and the dish is:

@@

Return loss measurements are similar to auto correlation measurement from a single HERA element. Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$. 
\section{\textbf{Results}}
\begin{figure}[ht]
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/RL_mag.png}
\end{minipage}
\vspace{0.1cm}
\begin{minipage}[b]{\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{plots/RL_phse.png}
\end{minipage}
\caption{Left: Magnitude of the return loss of power measured in between 100 to 200 MHz using vector network analyser. Right panel shows the corresponding phase. Return loss of the feed alone is shown in green while the same for the feed+dish assembly is shown in blue. Finally, the quantity of interest ${I_{rec}\over I_{sky}}$ is shown in red. In ideal condition 100\% of the sky power is to be received and ${I_{rec}\over I_{sky}} = 1$ or 0dB. Finite return loss at the antenna input deviate this quantity from its ideal value and ${I_{rec}\over I_{sky}} < 1$. Also, frequency dependence of the feed and the dish as well as the multiple reflections introduces the small scale fluctuations as seen in the red curve. }
% HERA feed design is derived from modified PAPER antenna and therefore the return loss closely relates to the PAPER antenna response with slight frequency shift. The return loss measured when the HERA feed is suspended over the dish is, however, show deviation from the feed performance. }
\label{fig:all_RL}
\end{figure}
\begin{figure}       
\centering
\includegraphics[width=\linewidth]{plots/H_dish_feed.png}
\caption{Delay spectrum of the HERA element (blue) the HERA feed (green) estimated by taking the Fourier transform of the measured return loss of power at the feed output. The feed, when suspended on the dish results in a more complex return loss and corresponding delay response is shown in the figure. After correcting the measurements from the transmission mode to reception mode by equation \ref{eq:power_ratio} the delay spectrum in the receiving mode is estimated (red). }
\label{fig:delay_spectrum}
\end{figure}

Figure \ref{fig:all_RL} shows the return loss measured between $100$ to
$200MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex. This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}. Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution. A number of systematic effects as well as mathematical artefacts that are critical to this measurements and corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.

\subsection{\textbf{Feed effect:zero delay correction}}
%At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.

While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}. This essentially represents a mismatch in between the feed and the 50 Ohm transmission line. In delay domain, this appears at the zero delay bin. The zero delay response is identical whether or not the feed is suspended on the dish and  Therefore, we measure this response by measuring the feed return loss alone while the feed is kept on the ground facing the sky. This results in feed return loss alone including the surrounding cage structure but excluding the dish response. While $\Gamma_{f}$ fraction of power is reflected off the feed, $1+\Gamma_{f}$ fraction of the power gets transmitted. In receiving mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected back in to the space while $1+\Gamma_{f}$ voltage enters the feed. In receiving mode, in delay domain, this appears at the zero delay bin.
The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated. Magnitude and phase of $\Gamma_{f}$ , $s_{11}$ and ${I_{rec}\over I_{sky}}$ is shown in figure \ref{fig:all_RL}.

\subsubsection{\textbf{Effect of antenna beam pattern and feed return loss}}
The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna. Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$. Since reflected signal results in system response in higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.  The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line. The complex feed antenna impedance is shown in the figure \ref{fig:feed_impedance}.
While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum. However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant. During observation, each HERA element is connected to an active balun similar to the ones used in the PAPER antenna (need reference) which provides greater than 10dB return loss of power at the feed output.These baluns are under further design improvements aiming at 10 to 20dB better imepedance match between the feed and the balun than the measurements presented here.  Our measurement is done using a vector network analyser for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{fig:all_RL}. This measurements are conservative estimate  for both $\Gamma_{f}$ and $s_{11}$.

\subsubsection{\textbf{Effect of measurement bandwidth and window function}}
Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the bandwidth of measurements. Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function. In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays. Therefore, appropriate windowing of the data is  necessary prior to taking the Fourier transform of the measured data. Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window. Windowing the data prior to Fourier transform significantly reduces the system response higher delays.  
\begin{figure}
\centering
\includegraphics[width=\linewidth]{plots/window_effect.png}
\caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz. Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window. The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
\label{fig:window}
\end{figure} 
%\subsubsection{\textbf{Delay spectrum of subbands}} 
%The red shifted 21cm power spectrum measurements could be divided into sub-bands around multiple frequencies corresponding to various redshifts. Assuming that the power spectrum evolved over the redshift range $\Delta z \>0.5$ (Zaldarriaga 2004, ) corresponding to a $5~MHz$ band width at $150~MHz$.
